---
title: "A shiny app that predict a son's height for a given father's height."
author: "Olivier Detandt"
date: "3 November 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction

This app is based on the father.son dataset in the UsingR library.

The goal is to predict the son'sheight for a given father height.

The model used is a simple linear model.

You can fin the app here:
https://odtbibi.shinyapps.io/fatherson_shiny_app/

The link to the gituhub repository is here
https://github.com/odtbibi/CourseraShinyAppProject


## How to use the app

In order to get the prediction, you will have to move the slider to the targeted father height.
The prediction of the son's height will be displayed below and also on the chart.
                
You also have the possiblity to display the confidence interval by checking the check box below the slider.
                        
## Code use in UI
```{r, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE}
library(shiny)
shinyUI(fluidPage(
        titlePanel("Predict the height of Men's children"),
        sidebarLayout(
                sidebarPanel(
                        sliderInput("sliderfheight", "What is the father height (in inch)?", 60, 75, value = 65),
                        checkboxInput("showInterval", "Show/Hide Confidence Interval", value = TRUE),
                        uiOutput("help")
                        
                ),
                mainPanel(
                        plotOutput("plot1"),
                        textOutput("predson")
                )
        )
))
```



## Code use in Server
```{r, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE}
brary(shiny)
library(UsingR)
shinyServer(function(input, output) {
        fit<-lm(sheight~.,data=father.son)
        newx <- seq(min(father.son$fheight), max(father.son$fheight), length.out=100)
        preds <- predict(fit, newdata = data.frame(fheight=newx),interval = "confidence")
        
        
        pred <- reactive({
                fheightInput <- input$sliderfheight
                predict(fit, newdata = data.frame(fheight = fheightInput))
        })
        output$plot1 <- renderPlot({
                fheightInput <- input$sliderfheight
                plot(father.son$fheight, father.son$sheight, xlab = "Father's Height",
                     ylab = "Son's Height", col="gray",bty = "o", pch = 12)
                abline(fit, col = "red", lwd = 2)
                if(input$showInterval){
                        polygon(c(rev(newx), newx), c(rev(preds[ ,3]), preds[ ,2]), col = "lightblue", border = NA)
                        lines(newx, preds[ ,3], lty = 'dashed', col = 'black')
                        lines(newx, preds[ ,2], lty = 'dashed', col = 'black')
                }
                points(fheightInput, pred(), col = "blue", pch = 16, cex = 2)
                
        })
      
        url <- a("You can find more info on my github repository here", href="https://github.com/odtbibi/CourseraShinyAppProject")
        output$help <- renderUI({
                tagList( url)
        })
        
        output$predson <- renderText({
                paste("The predicted Son Height is:",round(pred(),2), " inch")
        })
```
